---
output:
  pdf_document:
    latex_engine: pdflatex
    fig_caption: yes
    keep_tex: yes
documentclass: article
classoption: a4paper
geometry: "left=2cm,right=2cm,top=1cm,bottom=1cm"
header-includes: \usepackage{fancyhdr}
  \usepackage{booktabs,xcolor}
  \pagestyle{empty}
  \renewcommand{\headrulewidth}{0pt}
  \definecolor{L4A_orange}{RGB}{237,125,49}
  \fancypagestyle{plain}{\pagestyle{fancy}}  
  \setlength{\headheight}{20 pt}
  \setlength{\footskip}{20 pt}
  \setlength{\textheight}{0.9\textheight}
  \pagenumbering{gobble}
  \usepackage{librebaskerville}
  \usepackage[fontsize=10pt]{scrextend}
  \usepackage{float}
  \restylefloat{table}
  \usepackage{xcolor}
  \usepackage{multicol}
  \usepackage{wrapfig}
  \usepackage{mathptmx}
  \usepackage{caption}
  \setlength{\belowcaptionskip}{-10pt}
  \captionsetup{belowskip=0pt}
  \setlength{\parskip}{0cm}
  \setlength{\parindent}{0cm}
  \usepackage{lipsum}
  \usepackage{graphicx}
  \graphicspath{ {/Users/wb522556/WBG/Vincenzo Di Maro - Agile/06 - Agile Productivity Radar/DataWork/Task Allocation Check in/Report/Dummy/Outputs/Raw/} }
  \usepackage{array}
  \usepackage{enumitem}
  \usepackage{booktabs}
  \newcommand{\hideFromPandoc}[1]{#1}
  \hideFromPandoc{
    \let\Begin\begin
    \let\End\end
  }
  \usepackage{caption}
  \captionsetup{skip=0pt}


---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#run the backend code first before knitting
load("backend.RData")

options(tinytex.verbose = TRUE)
```


```{r backend, eval = FALSE, echo=FALSE}

#PART 3: Set folder folder paths --------------------------------------------

  #-------------#
  # Root folder #
  #-------------#
  
  # Add your username and folder path here (for Windows computers)
  # To find out what your username is, type Sys.getenv("USERNAME")
  if (Sys.getenv("USERNAME") == "wb522556") {
    
    projectFolder  <- "C:/Users/wb522556/Documents/GitHub/Agile_Productivity_Radar/DataWork/Task Allocation Check in/Report/Dummy/Code/R Markdown"
    
  }
```
 
---
title: "Your Tasks this Period | `r casename` "
author: "**Period**: `r startdate` to `r enddate`" 
output: pdf_document
---


\hrulefill
     \begin{center}
     \Large{\textbf{Executive Summary}}
     \end{center}


\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{5cm} m{5cm} m{5cm}}
     \begin {minipage} {5cm}
     \begin{center}
     \includegraphics[width=25mm, height=25mm]{icon1.jpg}
     \end{center}
     \end{minipage}
      &
     \begin {minipage} {5cm}
          \begin{center}
     \includegraphics[width=25mm, height=25mm]{icon2.jpg}
          \end{center}
     \end{minipage}
     &
     \begin {minipage} {5cm}
          \begin{center}
     \includegraphics[width=25mm, height=25mm]{icon3.jpg}
          \end{center}
     \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}


\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{0.5cm} m{4cm} m{0.5cm} m{4cm} m{0.5cm} m{4cm} m{0.5cm}}
    \begin {minipage} {0.5cm}
     \end{minipage}
      &
     \begin {minipage} {4cm}
     \Large{\textbf{\textcolor{blue}{\emph{`r admin_perc` percent}}} of your time was spent on administrative work.}
     \end{minipage}
      &
      \begin {minipage} {0.5cm}
     \end{minipage}
      &
     \begin {minipage} {4cm}
     \Large{\textbf{\textcolor{blue}{\emph{`r imp_act_perc` percent}}} of your time was spent on important work.}
     \end{minipage}
     &
    \begin {minipage} {0.5cm}
     \end{minipage}
      &
     \begin {minipage} {4cm}
     \Large{\textbf{\textcolor{blue}{\emph{`r analytical_perc` percent}}} of your time was spent on analytical projects.}
     \end{minipage}
     &
    \begin {minipage} {0.5cm}
     \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}


\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{5cm} m{5cm} m{5cm}}
     \begin {minipage} {5cm}
          \begin{center}
     \includegraphics[width=25mm, height=25mm]{icon5.jpg}
          \end{center}
     \end{minipage}
      &
     \begin {minipage} {5cm}
          \begin{center}
     \includegraphics[width=25mm, height=25mm]{icon6.jpg}
          \end{center}
     \end{minipage}
     &
     \begin {minipage} {5cm}
          \begin{center}
     \includegraphics[width=25mm, height=25mm]{icon4.jpg}
          \end{center}
     \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}


\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{0.5cm} m{4cm} m{0.5cm} m{4cm} m{0.5cm} m{4cm} m{0.5cm}}
         \begin {minipage} {0.5cm}
     \end{minipage}
      &
     \begin {minipage} {4cm}
     \Large{\textbf{\textcolor{blue}{\emph{`r meeting_perc` percent}}} of your time was spent on meetings.}
     \end{minipage}
      &
      \begin {minipage} {0.5cm}
     \end{minipage}
      &
     \begin {minipage} {4cm}
     \Large{\textbf{\textcolor{blue}{\emph{`r planned_perc` percent}}} of your time was spent on planned work.}
     \end{minipage}
     &
    \begin {minipage} {0.5cm}
     \end{minipage}
      &
     \begin {minipage} {4cm}
     \Large{\textbf{\textcolor{blue}{\emph{`r avg_act_dur` hours}}} was the average duration of each task you performed this period.}
     \end{minipage}
     &
    \begin {minipage} {0.5cm}
     \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}
    
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{8cm} m{8cm}}
     \begin {minipage} {8cm}
     \includegraphics[width=60mm, height=60mm]{wordcloud.jpg}
     \end{minipage}
      & 
      \begin{minipage}{8cm}
      \Large{This is a snapshot of all your activity descriptions by frequency of occurrence. \textbf{\textcolor{blue}{\emph{`r type_act_perc` percent}}} of your time was spent on \textbf{\textcolor{blue}{\emph{`r type_act_nme`}}}.}
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}


\newpage




\begin{center}
\Large{\textbf{Meetings}}
 \end{center}
 
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{10cm} m{7cm}}
     \begin {minipage} {10cm}
     \includegraphics[width=100mm, height=60mm]{withsomeone_plot.jpg}
     \end{minipage}
      & 
      \begin{minipage}{7cm}
      \Large{As a proportion of total time spent over the work-week, you have been engaged with: \textcolor{blue}{meetings} for \textbf{\textcolor{blue}{\emph{`r meeting_perc` percent}}} of the time, which totaled `r meeting_chh` hours.}
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}


\begin{center}
\Large{\textbf{Activity Type}}
 \end{center}
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{10cm} m{7cm}}
     \begin {minipage} {10cm}
     \includegraphics[width=100mm, height=60mm]{type_act_plot.jpg}
     \end{minipage}
      & 
      \begin{minipage}{7cm}
      \Large{As a proportion of total time spent over the work-week, you have been engaged with: \textcolor{blue}{`r type_act_nme`} for \textbf{\textcolor{blue}{\emph{`r type_act_perc` percent}}} of the time, which totaled `r type_act_chh` hours.}
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}


\begin{center}
\Large{\textbf{Projects}}
 \end{center}
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{10cm} m{7cm}}
     \begin {minipage} {10cm}
     \includegraphics[width=100mm, height=60mm]{cat_proj_plot.jpg}
     \end{minipage}
      & 
      \begin{minipage}{7cm}
      \Large{As a proportion of total time spent over the work-week, you have been engaged with: \textcolor{blue}{analytical projects} for \textbf{\textcolor{blue}{\emph{`r analytical_perc` percent}}} of the time, which totaled `r analytical_chh` hours.}
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}
      
\newpage


\begin{center}
\Large{\textbf{Administrative Work}}
 \end{center}
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{10cm} m{7cm}}
     \begin {minipage} {10cm}
     \includegraphics[width=100mm, height=60mm]{admin_act_plot.jpg}
     \end{minipage}
      & 
      \begin{minipage}{7cm}
      \Large{As a proportion of total time spent over the work-week, you have been engaged with: \textcolor{blue}{administrative tasks} for \textbf{\textcolor{blue}{\emph{`r admin_perc` percent}}} of the time, which totaled `r admin_chh` hours.}
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}
      
\begin{center}
\Large{\textbf{Planning}}
 \end{center}
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{10cm} m{7cm}}
     \begin {minipage} {10cm}
     \includegraphics[width=100mm, height=60mm]{planned_act_plot.jpg}
     \end{minipage}
      & 
      \begin{minipage}{7cm}
      \Large{As a proportion of total time spent over the work-week, you have been engaged with: \textcolor{blue}{planned tasks} for \textbf{\textcolor{blue}{\emph{`r planned_perc` percent}}} of the time, which totaled `r planned_chh` hours.}
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}


\begin{center}
\Large{\textbf{Importance of Tasks}}
 \end{center}
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{10cm} m{7cm}}
     \begin {minipage} {10cm}
     \includegraphics[width=100mm, height=60mm]{imp_act_s_plot.jpg}
     \end{minipage}
      & 
      \begin{minipage}{7cm}
      \Large{As a proportion of total time spent over the work-week, you have been engaged with: \textcolor{blue}{important tasks} for \textbf{\textcolor{blue}{\emph{`r imp_act_perc` percent}}} of the time, which totaled `r imp_act_chh` hours.}
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}
      
  \hrulefill


\newpage


\begin{center}
\huge{\textbf{Your Activities}}
 \end{center}
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{7cm} m{1cm} m{7cm}}
     \begin {minipage} {7cm}
          \begin{center}
      \textcolor{teal}{\textbf{\Large{Important Work (`r imp_act_perc` percent of your time)}}}
     \end{center}
     \end{minipage}
      & 
      \begin{minipage}{1cm}
      \end{minipage}
      &
      \begin{minipage}{7cm}
           \begin{center}
      \textcolor{cyan}{\textbf{\Large{Unimportant Work (`r 100-imp_act_perc` percent of your time)}}}
      \end{center} 
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}
  \hrulefill
      
   \begin{center}
    \Large{\textbf{Projects}}
    \end{center}
    \begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{4cm} m{3.5cm} m{4cm} m{3.5cm}}
          \begin {minipage} {4cm}
              \includegraphics[width=40mm, height=40mm]{cat_proj_pie2.jpg}
         \end{minipage}
    &
              \begin {minipage} {3.5cm}
      \large{\textit{Among work you classified as important, \textbf{\textcolor{teal}{`r cat_proj2_p` percent}} were \textbf{\textcolor{teal}{analytical projects}}.}}
             \end{minipage}
      &
            \begin {minipage} {4cm}
    \includegraphics[width=40mm, height=40mm]{cat_proj_pie1.jpg}
     \end{minipage}
      &
     \begin {minipage} {3.5cm}
      \large{\textit{Among work you classified as unimportant, \textbf{\textcolor{cyan}{`r cat_proj1_p` percent}} were \textbf{\textcolor{cyan}{analytical projects}}.}}
               \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}


   \begin{center}
    \Large{\textbf{Administrative vs Project Related}}
    \end{center}
    \begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{4cm} m{3.5cm} m{4cm} m{3.5cm}}
     \begin {minipage} {5cm}
         \includegraphics[width=40mm, height=40mm]{admin_act_pie2.jpg}
              \end{minipage}
              &
      \begin {minipage} {3.5cm}
    \large{\textit{Among work you classified as important, \textbf{\textcolor{teal}{`r admin_act2_p` percent}} was \textbf{\textcolor{teal}{project related work}}.}}
     \end{minipage}
      & 
      \begin{minipage}{4cm}
          \includegraphics[width=40mm, height=40mm]{admin_act_pie1.jpg}
      \end{minipage}
      &
      \begin{minipage}{3.5cm}
      \large{\textit{Among work you classified as unimportant, \textbf{\textcolor{cyan}{`r admin_act1_p` percent}} was \textbf{\textcolor{cyan}{administrative work}}.}}
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}
      
  \begin{center}
    \Large{\textbf{Meetings vs Independent Work}}
    \end{center}
    \begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{4cm} m{3.5cm} m{4cm} m{3.5cm}}
     \begin {minipage} {4cm}
         \includegraphics[width=40mm, height=40mm]{withsomeone_pie2.jpg}
         \end{minipage}
         &
         \begin {minipage} {3.5cm}
    \large{\textit{Among work you classified as important, \textbf{\textcolor{teal}{`r withsomeone2_p` percent}} was \textbf{\textcolor{teal}{independent work}}.}}
     \end{minipage}
      &
      \begin{minipage}{4cm}
          \includegraphics[width=40mm, height=40mm]{withsomeone_pie1.jpg}
            \end{minipage}
            &
       \begin{minipage}{3.5cm}
      \large{\textit{Among work you classified as unimportant, \textbf{\textcolor{cyan}{`r withsomeone1_p` percent}} were \textbf{\textcolor{cyan}{meetings}}.}}
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}
      
  \newpage
\begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{7cm} m{1cm} m{7cm}}
     \begin {minipage} {7cm}
          \begin{center}
      \textcolor{teal}{\textbf{\Large{Important Work (`r imp_act_perc` percent of your time)}}}
     \end{center}
     \end{minipage}
      & 
      \begin{minipage}{1cm}
      \end{minipage}
      &
      \begin{minipage}{7cm}
           \begin{center}
      \textcolor{cyan}{\textbf{\Large{Unimportant Work (`r 100-imp_act_perc` percent of your time)}}}
      \end{center} 
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}
  \hrulefill


  \begin{center}
    \Large{\textbf{Planned vs Unplanned}}
    \end{center}
    \begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{4cm} m{3.5cm} m{4cm} m{3.5cm}}
     \begin {minipage} {7cm}
         \includegraphics[width=40mm, height=40mm]{plan_act_pie2.jpg}
     \end{minipage}
     &
     \begin {minipage} {3.5cm}
    \large{\textit{Among work you classified as important, \textbf{\textcolor{teal}{`r plan_act2_p` percent}} were \textbf{\textcolor{teal}{planned}}.}}
     \end{minipage}
      &
      \begin{minipage}{4cm}
          \includegraphics[width=40mm, height=40mm]{plan_act_pie1.jpg}
      \end{minipage}
      &
      \begin{minipage}{3.5cm}
      \large{\textit{Among work you classified as unimportant, \textbf{\textcolor{cyan}{`r plan_act1_p` percent}} were \textbf{\textcolor{cyan}{unplanned}}.}}
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}


  \begin{center}
    \Large{\textbf{Activity Type}}
    \end{center}
    \begin{table}[h!]
     \begin{center}
     \begin{tabular}{m{4cm} m{3.5cm} m{4cm} m{3.5cm}}
     \begin {minipage} {4cm}
         \includegraphics[width=40mm, height=40mm]{type_pie2.jpg}
     \end{minipage}
     &
     \begin {minipage} {3.5cm}
    \large{\textit{Among work you classified as important, \textbf{\textcolor{teal}{`r type_pie2_p` percent}} were \textbf{\textcolor{teal}{`r type_pie2_n`}}.}}
     \end{minipage}
      & 
      \begin{minipage}{4cm}
    \includegraphics[width=40mm, height=40mm]{type_pie1.jpg}
      \end{minipage}
      &
      \begin{minipage}{3.5cm}
      \large{\textit{Among work you classified as unimportant, \textbf{\textcolor{cyan}{`r type_pie1_p` percent}} were \textbf{\textcolor{cyan}{`r type_pie1_n`}}.}}
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}