---
output:
  pdf_document:
    latex_engine: pdflatex
    fig_caption: yes
    keep_tex: yes
documentclass: article
classoption: a4paper
geometry: "left=0cm,right=0.2cm,top=1cm,bottom=0.5cm"
header-includes: \usepackage{fancyhdr}
  \usepackage{xcolor}
    \usepackage{librebaskerville}
  \usepackage[fontsize=10pt]{scrextend}
  \usepackage{float}
  \restylefloat{table}
  \usepackage{multicol}
  \usepackage{wrapfig}
  \usepackage{mathptmx}
  \usepackage{caption}
  \usepackage{lipsum}
  \usepackage{graphicx}
  \usepackage{caption}
  \usepackage{array}
  \usepackage{enumitem}
  \usepackage{booktabs}
  \usepackage{tabularx}
  \usepackage{colortbl}
  \usepackage{datetime}
  \usepackage[default,oldstyle,scale=0.95]{opensans}
  \renewcommand{\headrulewidth}{0pt}
  \fancypagestyle{plain}{\pagestyle{fancy}}  
  \setlength{\headheight}{12 pt}
  \setlength{\textheight}{0.9\textheight}
  \pagenumbering{gobble}
  \setlength{\belowcaptionskip}{-10pt}
  \captionsetup{belowskip=0pt}
  \setlength{\parskip}{0cm}
  \setlength{\parindent}{0cm}
  \graphicspath{ {"C:/Users/wb522556/WBG/Vincenzo Di Maro - Agile/06 - Agile Productivity Radar/DataWork/Task Allocation Check in/Report/Pilot/Outputs/Raw/"} }
  \newcommand{\hideFromPandoc}[1]
  \hideFromPandoc{
    \let\Begin\begin
    \let\End\end
  }
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#run the backend code first before knitting

load("~/GitHub/Agile_Productivity_Radar/DataWork/Task Allocation Check in/Report/Pilot/Code/R Markdown/backend.RData")

options(tinytex.verbose = TRUE)
```


```{r backend, eval = FALSE, echo=FALSE}

#PART 3: Set folder folder paths --------------------------------------------

  #-------------#
  # Root folder #
  #-------------#
  
  # Add your username and folder path here (for Windows computers)
  # To find out what your username is, type Sys.getenv("USERNAME")
  if (Sys.getenv("USERNAME") == "wb522556") {
    
    projectFolder  <- "C:/Users/wb522556/Documents/GitHub/Agile_Productivity_Radar/DataWork/Task Allocation Check in/Report/Pilot/Code/R Markdown"
    
  }
```
 
```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

  \begin{center}
     \begin {minipage} {20cm}
               \begin{center}
               \includegraphics[height=40mm]{head.jpg} \\
                       \Large{`r casename` || Between `r startdate` to `r enddate`}
               \end{center}
        \end{minipage}
        \end{center}

\begin{table}[H]
     \begin{center}
     \begin{tabular}{m{6cm} m{6cm} m{6cm}}
     \begin {minipage} {6cm}
               \begin{center}
               \includegraphics[width=30mm, height=30mm]{icon1.jpg} \\
          \Large{\textbf{`r admin_act_perc` percent}} \linebreak{\large{ of your time was spent on}} \linebreak{\Large{\textbf{`r admin_act_nme` work.}}} \\
          \vspace{10mm}
     \includegraphics[width=30mm, height=30mm]{icon4.jpg} \\
          \Large{\textbf{`r withsomeone_perc` percent}} \linebreak{\large{of your time was spent on}} \linebreak{\Large{\textbf{`r withsomeone_nme`.}}}
          \end{center}
     \end{minipage}
      &
     \begin {minipage} {6cm}
               \begin{center}
               \includegraphics[width=30mm, height=30mm]{icon2.jpg} \\
             \Large{\textbf{`r imp_act_s_perc` percent}} \linebreak{\large{of your time was spent on}} \linebreak{\Large{\textbf{`r imp_act_s_nme` work.}}} \\
             \vspace{10mm}
     \includegraphics[width=30mm, height=30mm]{icon6.jpg} \\
          \Large{\textbf{`r planned_act_perc` percent}} \linebreak{\large{of your time was spent on}} \linebreak{\Large{\textbf{`r planned_act_nme` work.}}}
          \end{center}
     \end{minipage}
     &
     \begin {minipage} {6cm}
          \begin{center}
               \includegraphics[width=30mm, height=30mm]{icon3.jpg} \\
         \Large{\textbf{`r cat_proj_perc` percent}} \linebreak{\large{of your time was spent on}} \linebreak{\Large{\textbf{`r cat_proj_nme` projects.}}} \\
         \vspace{10mm}
     \includegraphics[width=30mm, height=30mm]{icon5.jpg} \\
          \Large{\textbf{`r avg_act_dur` hours}} \linebreak{\large{was the average duration of}} \linebreak{\Large{\textbf{your tasks.}}}
          \end{center}
     \end{minipage} \\
          \vspace{1mm} \\
           \hline
           \vspace{1mm}
      \end{tabular}
           \begin{tabular}{m{2cm} m{6cm} m{6cm} m{2cm}}
      \multicolumn{4}{c}{\Large{How you described your activities | Word cloud}} \\
      \begin{minipage} {2cm}
     \includegraphics[width=20mm, height=60mm]{icon7.jpg}     
     \end{minipage}
     &
     \begin {minipage} {6cm}
     \includegraphics[trim=80 80 80 80, clip, width=60mm, height=60mm]{wordcloud.pdf}     
     \end{minipage}
      & 
      \begin{minipage}{6cm}
      \begin{flushleft}
      \Large{\textbf{`r freqmax_word_n`}} \linebreak{\large{were your most popular words to describe your activities.}}
      \end{flushleft}
      \end{minipage}
      &
      \begin{minipage} {2cm}
     \includegraphics[width=20mm, height=60mm]{icon8.jpg}     
     \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}

  \begin{center}
  \includegraphics[height=0.2in]{all_logos.jpg} \\
  \small{Produced on \today\ \currenttime}
  \end{center}
     
\newpage

\begin{table}[H]
     \begin{center}
     \begin{tabular}{m{11cm} m{7cm}}
     \begin {minipage} {11cm}
     \begin{center}
      \Large{\textbf{Meetings}} \\
     \includegraphics[width=110mm, height=60mm]{withsomeone_plot.pdf} 
          \end{center}
     \end{minipage}
      & 
      \begin{minipage}{7cm}
      \huge{\textbf{`r withsomeone_chh` hours}} \\
       \large{in a week (on average)} \\
      \Large{\textbf{on `r withsomeone_nme`}} \\
      \vspace{1mm} \\
      \Large{i.e. \textbf{`r withsomeone_perc` percent} of your total time recorded.}
      \end{minipage} \\
      \hline
      \vspace{0.1mm}
      \end{tabular}
      \begin{tabular}{m{7cm} m{11cm}}
      \begin{minipage}{7cm}
      \huge{\textbf{`r type_act_chh` hours}} \\
       \large{in a week (on average)} \\
      \Large{\textbf{on `r type_act_nme`}} \\
      \vspace{1mm} \\
      \Large{i.e. \textbf{`r type_act_perc` percent} of your total time recorded.}
      \end{minipage}
      &
      \begin {minipage} {11cm}
      \begin{center}
      \Large{\textbf{Activity Type}} \\
     \includegraphics[width=110mm, height=60mm]{type_act_plot.pdf}
          \end{center}
     \end{minipage} \\
      \hline
      \vspace{0.1mm}
      \end{tabular}
    \begin{tabular}{m{11cm} m{7cm}}
     \begin {minipage} {11cm}
     \begin{center}
     \Large{\textbf{Project Category}} \\
     \includegraphics[width=110mm, height=60mm]{cat_proj_plot.pdf}
     \end{center}
     \end{minipage}
      & 
      \begin{minipage}{7cm}
      \huge{\textbf{`r cat_proj_chh` hours}} \\
       \large{in a week (on average)} \\
      \Large{\textbf{on `r cat_proj_nme` projects.}} \\
      \vspace{1mm} \\
      \Large{i.e. \textbf{`r cat_proj_perc` percent} of your total time recorded.}
      \end{minipage} \\
      \hline
      \vspace{0.1mm}
      \end{tabular}
      \begin{tabular}{m{7cm} m{11cm}}
      \begin{minipage}{7cm}
      \huge{\textbf{`r admin_act_chh` hours}} \\
       \large{in a week (on average)} \\
      \Large{\textbf{on `r admin_act_nme` work.}} \\
      \vspace{1mm} \\
      \Large{i.e. \textbf{`r admin_act_perc` percent} of your total time recorded.}
      \end{minipage}
      &
     \begin {minipage} {11cm}
          \begin{center}
     \Large{\textbf{Administrative vs Technical}} \\
     \includegraphics[width=110mm, height=60mm]{admin_act_plot.pdf}
     \end{center}
     \end{minipage} \\
      \hline
      \vspace{0.1mm}
      \end{tabular}
      \end{center}
      \end{table}
      
\newpage

\begin{table}[H]
     \begin{center}
           \begin{tabular}{m{11cm} m{7cm}}
    \begin {minipage} {11cm}
        \begin{center}
     \Large{\textbf{Planned vs Unplanned}} \\
     \includegraphics[width=110mm, height=60mm]{planned_act_plot.pdf}
     \end{center}
     \end{minipage}
      &
    \begin{minipage}{7cm}
          \huge{\textbf{`r planned_act_chh` hours}} \\
       \large{in a week (on average)} \\
      \Large{\textbf{on `r planned_act_nme` tasks.}} \\
      \vspace{1mm} \\
      \Large{i.e. \textbf{`r planned_act_perc` percent} of your total time recorded.}
      \end{minipage} \\
      \hline
      \vspace{0.1mm}
      \end{tabular}
           \begin{tabular}{m{7cm} m{11cm}}
    \begin{minipage}{7cm}
      \huge{\textbf{`r imp_act_s_chh` hours}} \\
       \large{in a week (on average)} \\
      \Large{\textbf{on `r imp_act_s_nme` tasks.}} \\
      \vspace{1mm} \\
      \Large{i.e. \textbf{`r imp_act_s_perc` percent} of your total time recorded.}
      \end{minipage}
      & 
    \begin {minipage} {11cm}
    \begin{center}
     \Large{\textbf{Importance of Tasks}} \\
     \includegraphics[width=110mm, height=60mm]{imp_act_s_plot.pdf}
     \end{center}
     \end{minipage} \\
     \hline
      \end{tabular}
      \end{center}
      \end{table}

\newpage

\definecolor{Blue}{rgb}{0,0.7,1}
\definecolor{MidnightBlue}{rgb}{0.1,0.1,0.4}

\begin{table}[H]
     \begin{center}
          \huge{\textbf{Your Activities}} \\
          \vspace{1mm}
          \end{center}
          \begin{center}
     \begin{tabular}{m{8cm} m{1cm}  m{8cm}}
     \fcolorbox{MidnightBlue}{MidnightBlue}{
     \begin {minipage} {8cm}
          \begin{center}
    \textbf{\Large{\textcolor{white}{Important Work (`r imp_act_s_perc` percent of your time)}}}
     \end{center}
     \end{minipage}}
      & 
      \begin{minipage}{1cm}
      \end{minipage}
      &
      \fcolorbox{Blue}{Blue}{
      \begin{minipage}{8cm}
           \begin{center}
      \textbf{\Large{Unimportant Work (`r 100-imp_act_s_perc` percent of your time)}}
      \end{center} 
      \end{minipage}} \\
      \vspace{0.2mm}
      \end{tabular}
     \noindent\begin{tabular}{m{4cm} m{3.5cm} m{0.5cm} || m{0.5cm} m{3.5cm} m{4cm}}
      \multicolumn{6}{c}{\Large{\textbf{\underline{Activity Type}}}} \\
           \vspace{1mm} 
     \begin {minipage} {4cm}
         \includegraphics[width=40mm, height=40mm]{type_pie2.pdf}
     \end{minipage}
     &
     \begin {minipage} {3.5cm}
      \begin{flushright}
      \Large{\underline{\textbf{\textcolor{MidnightBlue}{`r type_pie2_p` percent}}}} \\
            \small{of your important activities were spent} \\
        \vspace{3mm} 
      \large{on `r type_pie2_n`} 
      \end{flushright}
     \end{minipage}
       &
          \begin{minipage} {0.5cm}
          \end{minipage}
      &
        \begin{minipage} {0.5cm}
          \end{minipage}
          &
      \begin{minipage}{3.5cm}
      \begin{flushleft}
      \Large{\underline{\textbf{\textcolor{Blue}{`r type_pie1_p` percent}}}} \\
            \small{of your unimportant activities were spent} \\
        \vspace{3mm} 
      \large{on `r type_pie1_n`} 
      \end{flushleft}
      \end{minipage}
      &
      \begin{minipage}{4cm}
          \includegraphics[width=40mm, height=40mm]{type_pie1.pdf}
      \end{minipage} \\
      \hline
           \vspace{1mm} 
      \end{tabular}
           \noindent\begin{tabular}{m{4cm} m{3.5cm} m{0.5cm} || m{0.5cm} m{3.5cm} m{4cm}}
     \multicolumn{6}{c}{\Large{\underline{\textbf{Projects}}}} \\
     \vspace{1mm} 
          \begin {minipage} {4cm}
      \includegraphics[width=40mm, height=40mm]{cat_proj_pie2.pdf}
         \end{minipage}
          &
        \begin {minipage} {3.5cm}
        \begin{flushright}
      \Large{\underline{\textbf{\textcolor{MidnightBlue}{`r cat_proj2_p` percent}}}} \\
            \small{of your important activities were spent} \\
        \vspace{3mm} 
      \large{on `r cat_proj2_n` Projects}
      \end{flushright}
             \end{minipage}
       &
          \begin{minipage} {0.5cm}
          \end{minipage}
      &
        \begin{minipage} {0.5cm}
          \end{minipage}
          &
            \begin {minipage} {3.5cm}
      \begin{flushleft}
      \Large{\underline{\textbf{\textcolor{Blue}{`r cat_proj1_p` percent}}}}
            \small{of your unimportant activities were spent} \\
                    \vspace{3mm} 
      \large{on `r cat_proj1_n` Projects} 
      \end{flushleft}
     \end{minipage}
      &
     \begin {minipage} {4cm}
    \includegraphics[width=40mm, height=40mm]{cat_proj_pie1.pdf}
      \end{minipage} \\
      \hline
           \vspace{1mm} 
      \end{tabular}
           \noindent\begin{tabular}{m{4cm} m{3.5cm} m{0.5cm} || m{0.5cm} m{3.5cm} m{4cm}}
      \multicolumn{6}{c}{\Large{\underline{\textbf{Administrative vs Technical}}}} \\
               \vspace{1mm} 
     \begin {minipage} {4cm}
         \includegraphics[width=40mm, height=40mm]{admin_act_pie2.pdf}
              \end{minipage}
              &
      \begin {minipage} {3.5cm}
      \begin{flushright}
      \Large{\underline{\textbf{\textcolor{MidnightBlue}{`r admin_act2_p` percent}}}} \\
            \small{of your important activities were spent} \\
                    \vspace{3mm} 
      \large{on `r admin_act2_n` Work}
      \end{flushright}
     \end{minipage}
       &
          \begin{minipage} {0.5cm}
          \end{minipage}
      &
        \begin{minipage} {0.5cm}
          \end{minipage}
          &
      \begin{minipage}{3.5cm}
      \begin{flushleft}
      \Large{\underline{\textbf{\textcolor{Blue}{`r admin_act1_p` percent}}}} \\
            \small{of your unimportant activities were spent on} \\
                    \vspace{3mm} 
      \large{on `r admin_act1_n` Work} 
      \end{flushleft}
      \end{minipage}
      &
      \begin{minipage}{4cm}
                \includegraphics[width=40mm, height=40mm]{admin_act_pie1.pdf}
      \end{minipage} \\
      \hline
           \vspace{1mm} 
      \end{tabular} 
                 \noindent\begin{tabular}{m{4cm} m{3.5cm} m{0.5cm} || m{0.5cm} m{3.5cm} m{4cm}}
      \multicolumn{6}{c}{\Large{\textbf{\underline{Meetings vs Independent Work}}}} \\
           \vspace{1mm} 
     \begin {minipage} {4cm}
         \includegraphics[width=40mm, height=40mm]{withsomeone_pie2.pdf}
         \end{minipage}
         &
         \begin {minipage} {3.5cm}
          \begin{flushright}
      \Large{\underline{\textbf{\textcolor{MidnightBlue}{`r withsomeone2_p` percent}}}} \\
      \small{of your important activities were spent} \\
              \vspace{3mm} 
      \large{on `r withsomeone2_n`}
      \end{flushright}
     \end{minipage}
       &
          \begin{minipage} {0.5cm}
          \end{minipage}
      &
        \begin{minipage} {0.5cm}
          \end{minipage}
          &
      \begin{minipage}{3.5cm}
            \begin{flushleft}
      \Large{\underline{\textbf{\textcolor{Blue}{`r withsomeone1_p` percent}}}} \\
            \small{of your unimportant activities were spent} \\
                    \vspace{3mm} 
      \large{on `r withsomeone1_n`}
      \end{flushleft}
          \end{minipage}
            &
       \begin{minipage}{4cm}
                 \includegraphics[width=40mm, height=40mm]{withsomeone_pie1.pdf}
      \end{minipage} \\
      \hline
           \vspace{1mm} 
      \end{tabular}
     \noindent\begin{tabular}{m{4cm} m{3.5cm} m{0.5cm} || m{0.5cm} m{3.5cm} m{4cm}}
      \multicolumn{6}{c}{\Large{\textbf{\underline{Planned vs Unplanned Work}}}} \\
           \vspace{1mm} 
     \begin {minipage} {4cm}
         \includegraphics[width=40mm, height=40mm]{plan_act_pie2.pdf}
     \end{minipage}
     &
     \begin {minipage} {3.5cm}
      \begin{flushright}
      \Large{\underline{\textbf{\textcolor{MidnightBlue}{`r plan_act2_p` percent}}}} \\
            \small{of your important activities were spent} \\
                    \vspace{3mm} 
      \large{on `r plan_act2_n` Work}
      \end{flushright}
     \end{minipage}
       &
          \begin{minipage} {0.5cm}
          \end{minipage}
      &
        \begin{minipage} {0.5cm}
          \end{minipage}
          &
      \begin{minipage}{3.5cm}
      \begin{flushleft}
      \Large{\underline{\textbf{\textcolor{Blue}{`r plan_act1_p` percent}}}} \\
            \small{of your unimportant activities were spent on} \\
                    \vspace{3mm} 
      \large{on `r plan_act1_n` Work} 
      \end{flushleft}
      \end{minipage}
      &
      \begin{minipage}{4cm}
                \includegraphics[width=40mm, height=35mm]{plan_act_pie1.pdf}
      \end{minipage}
      \end{tabular}
      \end{center}
      \end{table}

  \newpage
      
  \begin{center}
  \Huge{Your Data at a Glance}
  \end{center}
  \hrulefill
  
  \begin{center}
  \large{\textbf{The projects you worked on}}
  \end{center}
  
```{r df_proj}
library(knitr)
library(kableExtra)

names(df_proj)[names(df_proj) == "category.project"] <- "Category"
names(df_proj)[names(df_proj) == "instanceccategory.project"] <- "Your Data"
names(df_proj)[names(df_proj) == "instancecategory.project"] <- "All Data"
names(df_proj)[names(df_proj) == "freq.cinstancecategory.project"] <- "Your Data"
names(df_proj)[names(df_proj) == "freq.instancecategory.project"] <- "All Data"
names(df_proj)[names(df_proj) == "hh.actccategory.project"] <- "Your Data"
names(df_proj)[names(df_proj) == "hh.actcategory.project"] <- "All Data"
names(df_proj)[names(df_proj) == "avg.hhccategory.project"] <- "Your Data"
names(df_proj)[names(df_proj) == "avg.hhcategory.project"] <- "All Data"
names(df_proj)[names(df_proj) == "category.project.cpr"] <- "Your Data"
names(df_proj)[names(df_proj) == "category.project.pr"] <- "All Data"

kable(df_proj, 
      "latex", 
      booktabs = T, 
      row.names = FALSE,
      escape = F,
      align = "c") %>%
  kable_styling(font_size = 9) %>%
  column_spec(c(1,
                3,
                5,
                7,
                9,
                11)
              , border_right = T) %>%
    column_spec(c(2,
                4,
                6,
                8,
                10),
                bold = T) %>%
  add_header_above(c(" " = 1, 
                       "Instances" = 2, 
                       "Frequency (%)" = 2, 
                       "Total Time (hrs)" = 2,
                       "Average Time (hrs)" = 2,
                       "Total Time (%)" = 2), bold = T)
```
\hrulefill

  \begin{center}
  \large{\textbf{Your Meetings vs Independent Work}}
  \end{center}
  
```{r df_withsomeone}
library(knitr)
library(kableExtra)

names(df_withsomeone)[names(df_withsomeone) == "withsomeone"] <- "Category"
names(df_withsomeone)[names(df_withsomeone) == "instancecwithsomeone"] <- "Your Data"
names(df_withsomeone)[names(df_withsomeone) == "instancewithsomeone"] <- "All Data"
names(df_withsomeone)[names(df_withsomeone) == "freq.cinstancewithsomeone"] <- "Your Data"
names(df_withsomeone)[names(df_withsomeone) == "freq.instancewithsomeone"] <- "All Data"
names(df_withsomeone)[names(df_withsomeone) == "hh.actcwithsomeone"] <- "Your Data"
names(df_withsomeone)[names(df_withsomeone) == "hh.actwithsomeone"] <- "All Data"
names(df_withsomeone)[names(df_withsomeone) == "avg.hhcwithsomeone"] <- "Your Data"
names(df_withsomeone)[names(df_withsomeone) == "avg.hhwithsomeone"] <- "All Data"
names(df_withsomeone)[names(df_withsomeone) == "withsomeone.cpr"] <- "Your Data"
names(df_withsomeone)[names(df_withsomeone) == "withsomeone.pr"] <- "All Data"

kable(df_withsomeone, 
      "latex", 
      booktabs = T, 
      row.names = FALSE,
      escape = F,
      align = "c") %>%
  kable_styling(font_size = 9) %>%
  column_spec(c(1,
                3,
                5,
                7,
                9,
                11)
              , border_right = T) %>%
    column_spec(c(2,
                4,
                6,
                8,
                10),
                bold = T) %>%
  add_header_above(c(" " = 1, 
                       "Instances" = 2, 
                       "Frequency (%)" = 2, 
                       "Total Time (hrs)" = 2,
                       "Average Time (hrs)" = 2,
                       "Total Time (%)" = 2), bold = T)
```
\hrulefill

  \begin{center}
  \large{\textbf{Your Administrative vs Technical Work}}
  \end{center}
  
```{r df_admin}
library(knitr)
library(kableExtra)

names(df_admin)[names(df_admin) == "admin.activity"] <- "Category"
names(df_admin)[names(df_admin) == "instancecadmin.activity"] <- "Your Data"
names(df_admin)[names(df_admin) == "instanceadmin.activity"] <- "All Data"
names(df_admin)[names(df_admin) == "freq.cinstanceadmin.activity"] <- "Your Data"
names(df_admin)[names(df_admin) == "freq.instanceadmin.activity"] <- "All Data"
names(df_admin)[names(df_admin) == "hh.actcadmin.activity"] <- "Your Data"
names(df_admin)[names(df_admin) == "hh.actadmin.activity"] <- "All Data"
names(df_admin)[names(df_admin) == "avg.hhcadmin.activity"] <- "Your Data"
names(df_admin)[names(df_admin) == "avg.hhadmin.activity"] <- "All Data"
names(df_admin)[names(df_admin) == "admin.activity.cpr"] <- "Your Data"
names(df_admin)[names(df_admin) == "admin.activity.pr"] <- "All Data"

kable(df_admin, 
      "latex", 
      booktabs = T, 
      row.names = FALSE,
      escape = F,
      align = "c") %>%
  kable_styling(font_size = 9) %>%
  column_spec(c(1,
                3,
                5,
                7,
                9,
                11)
              , border_right = T) %>%
    column_spec(c(2,
                4,
                6,
                8,
                10),
                bold = T) %>%
  add_header_above(c(" " = 1, 
                       "Instances" = 2, 
                       "Frequency (%)" = 2, 
                       "Total Time (hrs)" = 2,
                       "Average Time (hrs)" = 2,
                       "Total Time (%)" = 2), bold = T)
```
\hrulefill

  \begin{center}
  \large{\textbf{Your Planned vs Unplanned Work}}
  \end{center}
  
```{r df_planned}
library(knitr)
library(kableExtra)

names(df_planned)[names(df_planned) == "planned"] <- "Category"
names(df_planned)[names(df_planned) == "instancecplanned"] <- "Your Data"
names(df_planned)[names(df_planned) == "instanceplanned"] <- "All Data"
names(df_planned)[names(df_planned) == "freq.cinstanceplanned"] <- "Your Data"
names(df_planned)[names(df_planned) == "freq.instanceplanned"] <- "All Data"
names(df_planned)[names(df_planned) == "hh.actcplanned"] <- "Your Data"
names(df_planned)[names(df_planned) == "hh.actplanned"] <- "All Data"
names(df_planned)[names(df_planned) == "avg.hhcplanned"] <- "Your Data"
names(df_planned)[names(df_planned) == "avg.hhplanned"] <- "All Data"
names(df_planned)[names(df_planned) == "planned.cpr"] <- "Your Data"
names(df_planned)[names(df_planned) == "planned.pr"] <- "All Data"

kable(df_planned, 
      "latex", 
      booktabs = T, 
      row.names = FALSE,
      escape = F,
      align = "c") %>%
  kable_styling(font_size = 9) %>%
  column_spec(c(1,
                3,
                5,
                7,
                9,
                11)
              , border_right = T) %>%
    column_spec(c(2,
                4,
                6,
                8,
                10),
                bold = T) %>%
  add_header_above(c(" " = 1, 
                       "Instances" = 2, 
                       "Frequency (%)" = 2, 
                       "Total Time (hrs)" = 2,
                       "Average Time (hrs)" = 2,
                       "Total Time (%)" = 2), bold = T)
```
\hrulefill

  \begin{center}
  \large{\textbf{Your Important vs Unimportant Work}}
  \end{center}
  
```{r df_imp}
library(knitr)
library(kableExtra)

names(df_imp)[names(df_imp) == "importance"] <- "Category"
names(df_imp)[names(df_imp) == "instancecimportance"] <- "Your Data"
names(df_imp)[names(df_imp) == "instanceimportance"] <- "All Data"
names(df_imp)[names(df_imp) == "freq.cinstanceimportance"] <- "Your Data"
names(df_imp)[names(df_imp) == "freq.instanceimportance"] <- "All Data"
names(df_imp)[names(df_imp) == "hh.actcimportance"] <- "Your Data"
names(df_imp)[names(df_imp) == "hh.actimportance"] <- "All Data"
names(df_imp)[names(df_imp) == "avg.hhcimportance"] <- "Your Data"
names(df_imp)[names(df_imp) == "avg.hhimportance"] <- "All Data"
names(df_imp)[names(df_imp) == "importance.cpr"] <- "Your Data"
names(df_imp)[names(df_imp) == "importance.pr"] <- "All Data"

kable(df_imp, 
      "latex", 
      booktabs = T, 
      row.names = FALSE,
      escape = F,
      align = "c") %>%
  kable_styling(font_size = 9) %>%
  column_spec(c(1,
                3,
                5,
                7,
                9,
                11)
              , border_right = T) %>%
    column_spec(c(2,
                4,
                6,
                8,
                10),
                bold = T) %>%
  add_header_above(c(" " = 1, 
                       "Instances" = 2, 
                       "Frequency (%)" = 2, 
                       "Total Time (hrs)" = 2,
                       "Average Time (hrs)" = 2,
                       "Total Time (%)" = 2), bold = T)
```
      
\newpage

  \begin{center}
  \large{\textbf{All your data}}
  \end{center}
  
```{r df_act}
library(knitr)
library(kableExtra)

names(df_act)[names(df_act) == "activity.descr"] <- "Activity Description"
names(df_act)[names(df_act) == "category.project"] <- "Project Category"
names(df_act)[names(df_act) == "withsomeone"] <- "Meetings"
names(df_act)[names(df_act) == "admin.activity"] <- "Administrative Work"
names(df_act)[names(df_act) == "importance"] <- "Importance"
names(df_act)[names(df_act) == "activity.duration"] <- "Duration (hrs)"
kable(df_act, 
      "latex", 
      booktabs = T, 
      row.names = FALSE,
      escape = F) %>%
  kable_styling(latex_options = "scale_down", font_size = 9)

```
\hrulefill
